\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-22 paper.qmd
Update the hex height and width notations

When $k=2$ which is assumed for hexagon binning, $y_{1,\text{max}}=1$ and $y_{2,\text{max}} = \frac{r_2}{r_1}\times \frac{2}{\sqrt{3}}$. (The $\frac{2}{\sqrt{3}}$ accounts for the different height ($h_b$) and width ($w_b$) of a regular hexagon.) (@fig-NLDR-scurve (a))

@@

To define a hexagonal grid across the \kD{} space, with hexagons of fixed height ($h_b$), width ($w_b$),  it is necessary to determine how many hexagons should be represented along each axis in the \kD{} space.

When $k=2$, the number of bins along the $x$ and $y$ axes, $b_1$ and $b_2$, is computed by considering the scaling factors ${r_1, r_2}$, along with the offset along the axes ($q_1$, $q_2$), and the height ($h_b$) and width ($w_b$) of a regular hexagon (@fig-NLDR-scurve (b)). ($b_1 = \frac{r_1 + q_1}{w_b}$, and $b_2 = \frac{r_2 + q_2}{0.75 \times h_b}$) where $0.75 \times h_b$ accommodate to have hexagons fill the entire 2D space without leaving any gaps between them.)

@@

Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($h_b$), width ($w_b$). Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to. This identification is done finding the nearest bin centroid for the \kD{} points by considering the \kD{} Euclidean distance.

When $k=2$, the starting coordinates $(s_1, s_2)$ mark the lower left of the grid. This is the bottom left bin centroid. By starting from there, points are generated to fill the grid accounting $b_1$, $b_2$, $w_b$, and $h_b$.

>>>>

When $k=2$ which is assumed for hexagon binning, $y_{1,\text{max}}=1$ and $y_{2,\text{max}} = \frac{r_2}{r_1}\times \frac{2}{\sqrt{3}}$. (The $\frac{2}{\sqrt{3}}$ accounts for the different height ($a_1$) and width ($a_2$) of a regular hexagon.) (@fig-NLDR-scurve (a))

@@

To define a hexagonal grid across the \kD{} space, with hexagons of fixed height ($a_1$), width ($a_2$),  it is necessary to determine how many hexagons should be represented along each axis in the \kD{} space.

When $k=2$, the number of bins along the $x$ and $y$ axes, $b_1$ and $b_2$, is computed by considering the scaling factors ${r_1, r_2}$, along with the offset along the axes ($q_1$, $q_2$), and the height ($a_1$) and width ($a_2$) of a regular hexagon (@fig-NLDR-scurve (b)). ($b_1 = \frac{r_1 + q_1}{a_2}$, and $b_2 = \frac{r_2 + q_2}{0.75 \times a_1}$) where $0.75 \times a_1$ accommodate to have hexagons fill the entire 2D space without leaving any gaps between them.)

@@

Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($a_1$), width ($a_2$). Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to. This identification is done finding the nearest bin centroid for the \kD{} points by considering the \kD{} Euclidean distance.

When $k=2$, the starting coordinates $(s_1, s_2)$ mark the lower left of the grid. This is the bottom left bin centroid. By starting from there, points are generated to fill the grid accounting $b_1$, $b_2$, $a_2$, and $a_1$.

### 2024-04-22 paper.tex
Update the hex height and width notations

When \(k=2\) which is assumed for hexagon binning,
\(y_{1,\text{max}}=1\) and
\(y_{2,\text{max}} = \frac{r_2}{r_1}\times \frac{2}{\sqrt{3}}\). (The
\(\frac{2}{\sqrt{3}}\) accounts for the different height (\(h_b\)) and
width (\(w_b\)) of a regular hexagon.) (Figure~\ref{fig-NLDR-scurve}
(a))

@@

To define a hexagonal grid across the \kD{} space, with hexagons of
fixed height (\(h_b\)), width (\(w_b\)), it is necessary to determine
how many hexagons should be represented along each axis in the \kD{}
space.

When \(k=2\), the number of bins along the \(x\) and \(y\) axes, \(b_1\)
and \(b_2\), is computed by considering the scaling factors
\({r_1, r_2}\), along with the offset along the axes (\(q_1\), \(q_2\)),
and the height (\(h_b\)) and width (\(w_b\)) of a regular hexagon
(Figure~\ref{fig-NLDR-scurve} (b)). (\(b_1 = \frac{r_1 + q_1}{w_b}\),
and \(b_2 = \frac{r_2 + q_2}{0.75 \times h_b}\)) where
\(0.75 \times h_b\) accommodate to have hexagons fill the entire 2D
space without leaving any gaps between them.)

@@

Define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(h_b\)), width (\(w_b\)). Each of the \kD{} points will
belong to a hexagonal bin. That is, for each \(y \in \mathbfit{Y}\), we
can (uniquely) identify the hexagon that the point belongs to. This
identification is done finding the nearest bin centroid for the \kD{}
points by considering the \kD{} Euclidean distance.

When \(k=2\), the starting coordinates \((s_1, s_2)\) mark the lower
left of the grid. This is the bottom left bin centroid. By starting from
there, points are generated to fill the grid accounting \(b_1\),
\(b_2\), \(w_b\), and \(h_b\).

>>>>

When \(k=2\) which is assumed for hexagon binning,
\(y_{1,\text{max}}=1\) and
\(y_{2,\text{max}} = \frac{r_2}{r_1}\times \frac{2}{\sqrt{3}}\). (The
\(\frac{2}{\sqrt{3}}\) accounts for the different height (\(a_1\)) and
width (\(a_2\)) of a regular hexagon.) (Figure~\ref{fig-NLDR-scurve}
(a))

@@

To define a hexagonal grid across the \kD{} space, with hexagons of
fixed height (\(a_1\)), width (\(a_2\)), it is necessary to determine
how many hexagons should be represented along each axis in the \kD{}
space.

When \(k=2\), the number of bins along the \(x\) and \(y\) axes, \(b_1\)
and \(b_2\), is computed by considering the scaling factors
\({r_1, r_2}\), along with the offset along the axes (\(q_1\), \(q_2\)),
and the height (\(a_1\)) and width (\(a_2\)) of a regular hexagon
(Figure~\ref{fig-NLDR-scurve} (b)). (\(b_1 = \frac{r_1 + q_1}{a_2}\),
and \(b_2 = \frac{r_2 + q_2}{0.75 \times a_1}\)) where
\(0.75 \times a_1\) accommodate to have hexagons fill the entire 2D
space without leaving any gaps between them.)

@@

Define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(a_1\)), width (\(a_2\)). Each of the \kD{} points will
belong to a hexagonal bin. That is, for each \(y \in \mathbfit{Y}\), we
can (uniquely) identify the hexagon that the point belongs to. This
identification is done finding the nearest bin centroid for the \kD{}
points by considering the \kD{} Euclidean distance.

When \(k=2\), the starting coordinates \((s_1, s_2)\) mark the lower
left of the grid. This is the bottom left bin centroid. By starting from
there, points are generated to fill the grid accounting \(b_1\),
\(b_2\), \(a_2\), and \(a_1\).
